---
title: "UCLA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(vars)
library(readxl)
library(corrgram)
library(zoo)
library(fanplot)
library(tseries)
library(forecast)
China <- read_excel("~/Desktop/科研/UCLA/report/data/经济数据.xlsx")
corrgram(China, order = TRUE, lower.panel = panel.shade, upper.panel = panel.cor, 
		text.panel = panel.txt, main = "Correlogram of data")

# variables
Date=China$Date
I_Added=China$I_Added
I_Revenue=China$I_Revenue
P_Revenue=China$P_Revenue
E_Revenue=China$E_Revenue
F_Invest=China$F_Invest
Estate_I=China$Estate_I
Estate_S=China$Estate_S
Retail=China$Retail
PPI=China$PPI
Budget=China$Budget
PMI_N=China$PMI_N
PMI_S=China$PMI_S
COV = China$COVID
XGuan = China$Baidu_Xinguan
Box = China$Box
export = China$export


# Box=China$Box

# after expurgation: remove P_Revenue and PMI_S
corrgram(data.frame(Retail,Estate_S,Box,I_Revenue,export), order = TRUE, lower.panel = panel.shade, upper.panel = panel.cor, 
		text.panel = panel.txt, main = "Correlogram of data")

# OLS
ols = lm(Retail ~ Estate_S+Box+I_Revenue+export)
summary(ols)
ols2 = lm(Estate_S ~ Retail+Box+I_Revenue+export)
summary(ols2)
ols3 = lm(export ~ Retail+Box+I_Revenue+Estate_S)
summary(ols3)

# ts variables
begin = c(2007,1)
I_Added = ts(China$I_Added, start = begin, end = c(2020,7), frequency = 12)
I_Revenue = ts(China$I_Revenue, start = begin, end = c(2020,7), frequency = 12)
E_Revenue = ts(China$E_Revenue, start = begin, end = c(2020,7), frequency = 12)
F_Invest = ts(China$F_Invest, start = begin, end = c(2020,7), frequency = 12)
Estate_I = ts(China$Estate_I, start = begin, end = c(2020,7), frequency = 12)
Estate_S = ts(China$Estate_S, start = begin, end = c(2020,7), frequency = 12)
Retail = ts(China$Retail, start = begin, end = c(2020,7), frequency = 12)
PPI = ts(China$PPI, start = begin, end = c(2020,7), frequency = 12)
Budget = ts(China$Budget, start = begin, end = c(2020,7), frequency = 12)
PMI_N = ts(China$PMI_N, start = begin, end = c(2020,7), frequency = 12)
COV = ts(China$COVID, start = begin, end = c(2020,7), frequency = 12)
XGuan= ts(China$Baidu_Xinguan, start = begin, end = c(2020,7), frequency = 12)
Baidu_WZ = ts(China$Baidu_WZ, start = begin, end = c(2020,7), frequency = 12)
Box = ts(China$Box, start = begin, end = c(2020,7), frequency = 12)
export = ts(China$export, start = begin, end = c(2020,7), frequency = 12)




### ts data frame
China_ts = data.frame(Retail,Estate_S,Box,I_Revenue,export)
China_ts = na.spline(China_ts, na.rm = TRUE)


# ###Differencing (to make it stationary) and diagnostic
# I_Revenue = diff(I_Revenue);
pp.test(China_ts[,1])

# Estate_S = diff(Estate_S);
pp.test(China_ts[,2])

# Retail = diff(Retail);
pp.test(China_ts[,3])

pp.test(China_ts[,4])

pp.test(China_ts[,5])


autoplot(cbind(Retail,Estate_S,export), xlab = "Year", ylab = "Index", main = "The trend of the three variables")


### lag selection
lagselect = VARselect(China_ts, lag.max = 10, type = "const")
lagselect$selection

### VAR model
lag = 2
Vmodel = VAR(China_ts, p = lag,type = "const", season = NULL, exogen = NULL)
summary(Vmodel)


### forecast
forecast = predict(Vmodel, n.ahead = 12, ci = 0.95)
tail(China_ts)
forecast
fanchart(forecast, names = "Estate_S", main = "Fanchart of The Total Real Estate Sales", ylab = "Estate_S")
fanchart(forecast, names = "Retail", main = "Fanchart of The Total Retail Sales of Consumer Goods", ylab = "Retail")
fanchart(forecast, names = "export", main = "Fanchart of Exports", ylab = "export")
### diagnostic
##Autocorrelation
serial.test(Vmodel, lags.pt = 10, type = "PT.asymptotic")
